## Housing Prices Analysis
This analysis uses a dataset relative to houses prices in the USA.

The objective is to analyse which are the factors that contribute the most to the prices of houses.

First of all I import libraries,import the data and visualize it
```{r}
library(dplyr)
library(ggplot2)
df<-read.csv("C:/Users/s1720/OneDrive/Desktop/GitHub/DataSet/Housing.csv")
str(df) #Checking data structure
head(df) #Importing the first values of each column
```
Checking if the dataset needs cleaning
```{r}
mean(df$price)#If there are non numerical values we get NA
mean(df$area)
mean(df$bedrooms)
mean(df$bathrooms)
mean(df$stories)
mean(df$parking)
sum(is.na(df)) #Checking if there are NA values in general including char columns
sapply(df,length) #Checking that the values have the same length
df <- df[!duplicated(df), ]  #Eliminate duplicates if present
```
Since there needs to be no cleaning I go on and convert the yes and no values into 0 and 1 dummy variables (0, 1 and 2 in the case of furniture)
```{r}
#First the variables with yes and no
binary_cols <- c("mainroad", "guestroom", "basement", "hotwaterheating",
                 "airconditioning", "prefarea")
df[binary_cols]<-lapply(df[binary_cols],function(x) ifelse(x=="yes",1,0))

#Second the furniture variable
df[["furnishingstatus"]]<-lapply(df[["furnishingstatus"]],function(x) ifelse(x=="furnished",2,ifelse(x=="semi-furnished",1,0)))
#str(df)
df$furnishingstatus <- unlist(df$furnishingstatus) #Changing the column from list to num
str(df)
```
Then I calculate summary statistics and visualize a histogram of the data
```{r}
summary(df[,c("price","area","bedrooms","bathrooms","stories")])
hist(df$price)
```

As we can see the prices of the houses go from 1.750.000,00 to 13.300.000,00$, with a median of 4.340.000,00 dollars.
The area has a minimum of 1.650 sq. ft. and a maximum of 16.200, the median is 4600.
In both cases the median is smaller than the mean suggesting the presence of a skewness to the left and of some values
extremely high values that noticeably increase the mean.

Now there I regress the prices on all the other variables
```{r}
model<-lm(price~ area+bedrooms+bathrooms+stories+mainroad+guestroom+basement+hotwaterheating+airconditioning+parking+prefarea+furnishingstatus, data=df)
summary(model)
```
All variables, aside from the number of bedrooms, are significantly different from 0 at the 5% significance level.

Now I eliminate the number of bedrooms.
```{r}
model<-lm(price~ area+bathrooms+stories+mainroad+guestroom+basement+hotwaterheating+airconditioning+parking+prefarea+furnishingstatus, data=df)
summary(model)
```
Now all explanatory variables of the model are significantly different from zero at  the 0.05 significance level.
In this model we see the highest effect on price is given by the number of bathrooms, the presence of air conditioning,
of hot water heating, the presence in a preferential area and the presence of an access to a mainroad.
The R-squared is quite high suggesting a good capacity of the model to explain the prices of housing in America.

Said Mouhtaram

Source of the Dataset:
https://www.kaggle.com/datasets/yasserh/housing-prices-dataset/data